% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download
% helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document}

\name{Easton Wei}
% \address used twice to have two lines of address
%\address{345 Park Ave, San Jose, CA 95110}
%\address{$\vert$ 3358 Napoli Pl, San Jose, CA 95135 $\vert$
% shengwei@ucla.edu $\vert$ (310)745-9762 $\vert$  \quad \quad \quad
% \quad  \quad \quad \quad \quad \quad \quad}


\begin{resume}

  %\section{OBJECTIVE}  Tenure Track Assistant Professor in Computer Science
  %\section{Contact \\ Information}
  %Adobe Research  \hskip 10em Phone: (310)745-9762 \\
  %345 Park Ave \hskip 11.1em E-mail: \nolinkurl{shengwei@ucla.edu} \\
  %San Jose, CA 95110, USA \hskip 5.6em Web:
  % \url{http://sites.google.com/site/sweiucla}
  %\vskip -0.1in

  \section{Contact \\ Information}
  41 Nestlewood Way \hfill Phone (Parents): (310)745-9762 \\
  Princeton, NJ 08540 \hfill E-mail: \nolinkurl{eastonwei12@gmail.com} \\
  USA \hfill Web: \url{https://sites.google.com/view/chemistryforbeginners}
  \vskip -0.1in

  %\section{Research \\ Interests}
  %
  %{\bf Hardware and System Security; Multimedia Systems; Multimedia Security. }
  %\vskip -0.1in
  \section{Education}
  {\bf  Village Elementary School}, West Windsor, NJ  \hfill 2020 -- Present
  \vskip 0.05in
  \begin{itemize}
    \item 4th to 5th grade
      %\quad \quad - Dissertation: Consistency-based System Security Techniques
  \end{itemize}
  %
  \vskip -0.05in
  {\bf Dutch Neck Elementary School}, West Windsor, NJ \hfill 2018 -- 2020
  \vskip 0.05in
  \begin{itemize}
    \item  2nd to 3rd grade
  \end{itemize}

  \vskip -0.05in
  {\bf Maxey Elementary School}, Lincoln, NE \hfill 2017 -- 2018
  \vskip 0.05in
  \begin{itemize}
    \item  Kindergarten to 1st grade
  \end{itemize}


  \section{Awards}
  \begin{itemize}[leftmargin=*]
    \item {\bf National Gold Medal}, Piano Level 5, Royal
      Conservatory of Music, August 2021.
    \item {\bf Northeast Region Gold Medal}, Piano Level 4, Royal
      Conservatory of Music, Sept. 2020.
    \item {\bf Gold Award}, Village School PTA Virtual S.T.E.A.M Fair, 2021.
    \item {\bf ``Best Motor Skills" Award}, FIRST LEGO League Junior
      Competition, November 2018.
  \end{itemize}

  \section{Academics}
  {\bf  Math:} Self learned middle/high school math courses, such as
  Prealgebra, Algebra, Number Theory, Counting \& Probability, and Geometry.
  \vskip 0.05in
  \begin{itemize}
    \item MAP test scores (percentile) : \textbf{279 (99\%)} - Fall
      2021, Grade 5; \textbf{292 (99\%)} - Spring 2021, Grade 4;
      \textbf{276 (99\%)} - Fall 2020, Grade 4; \textbf{248 (99\%)} -
      Fall 2019, Grade 3; \textbf{253 (99\%)} - Spring 2019, Grade 2;
      \textbf{232 (99\%)} - Fall 2018, Grade 2.
      %  \item Start Strong 2021 Math test score: 25/25
  \end{itemize}

  {\bf  Chemistry:} Self learned high school chemistry and organic chemistry.
  \vskip 0.05in
  \begin{itemize}
    \item Attending AP Chemistry and Chemistry Olympiad courses
      offered by Dr. Steven Chen.
    \item Leading a team to participate in the ``You be the Chemist"
      challenge 2021-2022, organized by the Chemical Educational Foundation.
    \item Authoring and hosting a personal ``Introduction to
      Chemistry" website
      (\url{https://sites.google.com/view/chemistryforbeginners}),
      with a rich set of self-presented/authored chemistry video
      tutorials, articles, and experiment logs.
  \end{itemize}

  {\bf  Reading:} Proficient reader with level U/V/W according to the
  Spring 2021 assessment.

  \section{Art/Music}
  {\bf  Piano:} 6 years of experience, National Gold Medal (Level 5,
  2021) and Northeast Region Gold Medal (Level 4, 2020), Royal
  Conservatory of Music.

  {\bf  Violin:} 2 years of experience, participating in the
  orchestra and being a first violinist in the Chamber Club at Village School.

  \section{Sports/Hobbies}

  {Tennis/ice skating/skiing/swimming/Rubik's cube}

  % \section{References upon Request: } Dr. Chen, Kairy/Blickenstaff,
  % Ms. Orlovsky

\end{resume}
\end{document}
