\documentclass[11pt,letterpaper,sans]{moderncv}

\moderncvcolor{black} % 'blue' (default), 'orange', 'green', 'red',
\moderncvstyle{banking} % 'casual', 'classic', 'oldstyle' 'banking', 'fancy'
% 'purple', 'grey' and 'black'

\usepackage[scale=0.75]{geometry} % Reduce document margins
\addtolength{\voffset}{-3.5em}
\addtolength{\textheight}{7em}
\setlength{\hintscolumnwidth}{2cm} % width of dates column

\newcommand{\entry}[6]%
{\cventry[0.85em]{#4}{#3}{#2}{#1}{#5}{#6}} % banking
\lfoot{\emph{Last updated \today}}

\newcommand{\subtext}[1]{\bgroup\footnotesize\rmfamily\color{black!70}#1\egroup}
\newcommand{\previous}[1]{\bgroup\color{black}\bfseries#1\egroup}

\newcommand{\job}[4]{\smallskip\cvitemwithcomment{#2}{#1}{#3}%
\unskip\subtext{#4}\medskip}

\newcommand{\pub}[2]{\cvlistitem{#1. \\ \subtext{#2}}\smallskip}
\newcommand{\paper}[3]{\pub{#1}{#2. \arxiv{#3}.}}

\name{}{Easton Wei}
\lfoot{\emph{Last updated \today}}

\begin{document}
\makecvtitle
\section{Contact Information}
10 Barnyard Ct \hfill Princeton, NJ 08540 \\
E-mail: \nolinkurl{eastonwei12@gmail.com} \hfill GitHub:
\url{github.com/extouchtriangle}
\vskip -0.1in
\section{Education}
\entry{Fall 2022 -- Summer 2025}{WW-P Community Middle School}{Student}{}{}{}
\section{Internships}
\entry{Jun -- Aug 2025}{WINLAB Summer Intership}{Intern}{}{}{Worked on the
  project ``Visual
  Perception for AR Glasses'', and did detailed benchmarking on the effect of
  decreasing the framerate of an input recording on the accuracy of
  two different SLAMs.
  The end goal was to investigate ways to decrease the power usage of
  on-device data collection. Project page: \\
  \url{extouchtriangle.github.io/winlab_summer_2025/weekly.html
}}
\section{Awards and Results}
\subsection{Mathematics}
\begin{itemize}
  \item Strong background in algebra, combinatorics, number theory, and
    Euclidean geometry.
  \item Also studied linear algebra and multivariable calculus.
\end{itemize}
\vskip 0.1in
\entry{May 2025}{MathCounts National Competition}{21st out of 224
competitors}{}{}{The top 4 middle-school students in each of 56 U.S. states
  and territories
are selected to participate in the National Competition.}
\entry{March 2025}{MathCounts NJ State Competition}{4th place}
{}{}{MathCounts is a middle-school competition that
  involves an individual round and a team round.
  The top 10 individual competitors compete in a buzzer-based round.
  The top 4 finishers after the buzzer-based round advance to the
National Competition.}
\entry{February 2025}{AIME I}{10/15}{}{}{Top scorers on the AMC 10
  and AMC 12 are invited to participate in the AIME. While the
  competition assesses similar areas compared to the AMC 10/12,
the problems are significantly more difficult.}
\entry{November 2024}{PUMaC (Princeton University)}{}{}{}{
  \vskip -0.15in
  PUMaC is a high-school mathematics competition, offered
  in-person at Princeton University. The 8-person team was selected
  from the student body of WW-P High School North and WW-P Community
  Middle School.
}
\entry{November 2024}{MMATHS (Yale University)}{3rd place team}{}{}{MMATHS
  is a high-school mathematics competition consisting of an individual round
  and a team round, available to be taken at multiple venues across the
  country. The 6-person team was selected
  from the student body of WW-P High School North and WW-P Community
  Middle School.
}
\entry{November 2024}{AMC 10B}{138/150, top 1\%}{Honor Roll of Distinction}{}
{The AMC 10 is open to all American students in grades 10 and younger.
  The problems cover concepts including algebra, combinatorics, geometry, and
number theory.}
\entry{May 2024}{ARML (Pennsylvania State University)}{Participated
through WW-P High School North}{}{}{
  The ARML is a high-school math competition offered at
  Pennsylvania State University. Each high school can send
  1--2 teams to the event. 30 students (split into two teams)
  were selected from the WW-P and Princeton school districts
  to participate in this event.
}
\entry{May 2024}{MathCounts National Competition}{41st out of 224
competitors}{}{}{The top 4 middle-school students in each of 56 U.S. states
  and territories
are selected to participate in the National Competition. }
\entry{March 2024}{MathCounts NJ State Competition}{2nd
place}{}{}{MathCounts is a middle-school competition that
  involves an individual round and a team round.
  The top 10 individual competitors compete in a buzzer-based round.
  The top 4 finishers after the buzzer-based round advance to the
National Competition.}
\entry{February 2024}{AMC 8}{24/25, top 1\%}{Honor Roll of Distinction}{}{
  The AMC 8 is a middle-school mathematics competition
  open to be taken by American students in grades 8 and younger.
  It assesses geometry, number theory, algebra, and combinatorics.
}
\subsection{Science}
\begin{itemize}
  \item Solid background in chemistry, biology, physics, and astronomy.
\end{itemize}
\vskip 0.1in
\entry{February 2025}{PRISMS Science Bowl}{1st place}{}{team captain}
{A state-wide science competition organized by
  the Princeton International School of Math and Science (PRISMS).
}
\entry{May 2024}{Science Olympiad National Competition (Michigan
State University)}{}{}{}{
  \vskip -0.15in
  The first-place team at each state competition advances to the national
  competition.
}
\entry{March 2024}{NJ State Science Olympiad Competition}{1st place}{}{}{
  Science Olympiad is a middle-school science competition
  that features multiple events, with questions based on physics, chemistry,
  biology, geology, and engineering.
}
\section{Skills}
\subsection{General Computer Science}
\begin{itemize}
  \item Watched lecture videos for MIT 6.006 (Introduction to Algorithms),
    offered by the MIT CSAIL department.
  \item Familiar with Python, Arch Linux, and Ubuntu Linux. % and c++
\end{itemize}
\subsection{Machine Learning}
\begin{itemize}
  \item Studied course materials in CS231n (Deep Learning for Computer
    Vision), offered by the Computer Science Department
    at Stanford University.

  \item Familiar with PyTorch, NumPy, Convolutional Neural Networks, Recurrent
    Neural Networks,
    Transformers (Multihead Self-Attention, Positional Encoding),
    Generative Adversarial Networks,
    Self-Supervised Learning
\end{itemize}
\subsection{Chemistry}
\begin{itemize}
  \item Studied General Chemistry, AP Chemistry, and Organic Chemistry
\end{itemize}
\section{Hobbies}
Tennis, Violin, Computer Programming, Rubik's Cube
\vskip 0.1in
\entry{May 2023}{GCU Spring 2023 (Speedcubing)}{14.20 second average
3x3x3 time}{}{}{
  Competitors solved
  Rubik's cubes (and similar puzzles) as fast as they could.
}
\entry{February 2023}{Central Jersey Regional Orchestra}{Participated in
String Orchestra}{}{}{
  60 violinists from the Central Jersey region were
  selected to play the violin in the Regional Orchestra.
}
\end{document}
